Paleoenvironmental models for Australia and the impact of aridification on blindsnake diversification

### 2023-05-29 manuscript.Rmd
update manuscript

Advances in phylogenetic comparative methods and paleoenvironmental reconstructions allow us to better understand regional diversification dynamics. The influence of temperature on diversification rates has been empirically tested with birth-death models [@condamineMacroevolutionary2013;@kergoatOpposite2018;@condamineClimate2019;@rollandContribution2019]. Traditionally, these temperature data are reconstructed (interpolated) based on conversion of global concentration of oxygen isotopes [@condamineMacroevolutionary2013]. The relationship between diversification rates and aridity, however, have been attributed to some proxies such as the timing of aridification or global temperature rather than quantifying the extent of regional aridity itself [@dornStrange2014;@deepakAridification2018;@catulloAridification2014;@fujitaDiversification2010;@pepperGenetic2011;@pepperPalaeoclimate2011;@oliverIndependent2014;@oliverContrasting2014;@owenHow2017;@crispHow2013;@toussaintUnveiling2015].

>>>>

Advances in phylogenetic comparative methods and paleoenvironmental reconstructions allow us to better understand regional diversification dynamics. The influence of temperature on diversification rates has been empirically tested with birth-death models [@condamineMacroevolutionary2013;@kergoatOpposite2018;@condamineClimate2019;@rollandContribution2019]. Global paleotemperature data for these analyses was first presented in @condamineMacroevolutionary2013, whereby relative proportions of different oxygen isotopes in samples of benthic foraminifer shells [@zachosEarly2008] over geological time was converted to absolute temperature using a formula from @epsteinRevised1953. The relationship between diversification rates and aridity, however, have been attributed to some proxies such as the timing of aridification or global temperature rather than quantifying the extent of regional aridity itself [@dornStrange2014;@deepakAridification2018;@catulloAridification2014;@fujitaDiversification2010;@pepperGenetic2011;@pepperPalaeoclimate2011;@oliverIndependent2014;@oliverContrasting2014;@owenHow2017;@crispHow2013;@toussaintUnveiling2015].
